% !TEX program = xelatex
\input{cv_prelude}

\begin{document}

\title{\url{https://github.com/Ytrewq13}}
\author{Sam Robert Whitehead}

\maketitle

\pagestyle{empty}
\thispagestyle{empty}

\href{tel:(+86)13612808157}{Tel: (+86)136-1280-8157} \hfill
\href{mailto:SWhitehead1999@outlook.com}{Email: SWhitehead1999@outlook.com}
\\
As a Software Engineer at a small quantitative trading firm in Shenzhen, I
am constantly exposed to a wide range of technologies and new challenges. My
growing expertise includes \emph{system administration, tooling development,
and Linux internals}. Outside of work, I have \emph{extensive experience with
Linux}, which has enhanced my working efficiency. Looking to \emph{return to
the UK} to contribute my knowledge back home.

\section{Education}
\subsection{University of Nottingham \hfill 2018-09 -- 2022-07}
Degree: \textbf{Master of Science} in Computer Science
        \hfill
        First class honours (4.0 GPA)
        \begin{itemize}
            \item \emph{Algorithms and data structures} in C, Java, C++,
                Python, and Haskell.
            \item Functional Programming and OOP.
            \item \emph{Compiler design} and implementation.
            %\item Robotics programming.
            \item \emph{Information Visualization}, Data modeling and Analysis.
            \item Dissertation: \emph{Operating System development} --
                    ARM CPU modes and register setup,
                    Graphics driver,
                    System calls,
                    File systems.
        \end{itemize}
%\subsection{NEW College Pontefract \hfill 2016-09 -- 2018-07}
%\textbf{A-levels}: Achieved 3 A-Levels, with grades A*AA.
%           \begin{tabular}{cccc}
%               \textbf{Subject} & \textbf{Exam Board} & \textbf{AS/A2} &
%               \textbf{Grade}\\
%               Mathematics & AQA & A2 & A* \\
%               Further Mathematics & AQA & A2 & A \\
%               Computer Science & OCR & A2 & A \\
%               Physics & AQA & AS & A
%           \end{tabular}
%   \subsection{Kettlethorpe High School
%       \hfill 2011-09 -- 2016-07}
%       Achieved 10 GCSEs, including 5 A* grades and 5 A grades.
%       upon request).

\section{Work Experience}
\subsection{Software Engineer - CapitalAdd/铭珈资本 (Shenzhen) \hfill 2023-06 --
present}
\begin{itemize}
%    \item Prepared and used automated installation and configuration for
%        Ubuntu servers including Ubuntu server autoinstaller and Ansible
%        playbooks.
    \item Prepared and used \emph{automated installation} and configuration for
        Ubuntu servers, including using the Ubuntu server autoinstaller and
        \emph{Ansible playbooks}. Learned how to streamline server deployment
        and configuration through \emph{automation}.
%    \item Wrote various user-friendly and high-performance tools in Python
%        and C++.
    \item Wrote various user-friendly and \emph{high-performance tools} in
        Python and C++, Improving my skills in software development principles.
%    \item Researched and prepared for installation of a clustered network
%        storage solution using BeeGFS. Planned server hardware and tested
%        various network layouts.
    \item Researched and prepared for installation of a \emph{distributed
        network storage solution} using BeeGFS. Planned server \emph{hardware}
        and tested various network layouts, gaining knowledge on scalable
        storage solutions and network architecture. \emph{Took ownership} of
        the project and \emph{worked independently}.
    \item Deployed an open-source web UI for OpenAI API using
        \emph{docker-compose for orchestration}, allowing our office to access
        AI assistants, bypassing the GFW by using an intermediate VPS as a
        proxy. Taught myself Docker, \emph{reverse-proxy}, and \emph{FastAPI}
        for extending the available technologies.
\end{itemize}

\subsection{English Teacher - HouHai English (Shenzhen) \hfill 2022-12 --
2023-05}
%Prepared and delivered lessons to classes of up to 10 students between
%5-11 years old. Wrote feedback on students' performance to evaluate their
%progression.
Prepared and delivered lessons to classes of up to 10 students between 5-11
years old. \emph{Developed innovative teaching methods} to engage young
learners, including interactive games and competitive activities. Observed and
assessed students' progress, providing \emph{constructive feedback} to enhance
their learning experience. Learned to adapt lessons to meet the diverse needs
of individual students, fostering an inclusive classroom environment. Greatly
improved my \emph{communication skills} and self-confidence, gaining
\emph{public speaking and presentation} experience.

\section{Projects}
        \begin{itemize}
            \item \href{https://github.com/Ytrewq13/mandelbrotc}{Mandelbrot generator in C}
    -- \emph{Libpng} for storing images, complex arithmetic and
    \emph{multithreading} in C.
            \item \href{https://github.com/Ytrewq13/mazemaker.git}{Maze generator and solver in Java and Javascript}
    -- \emph{Optimisation} of Javascript rendering code, A* search algorithm.
            \item Major \emph{contributor} to
                \href{https://github.com/nsxiv/nsxiv.git}{nsxiv} (Revival of
                image viewer \href{https://github.com/muennich/sxiv}{sxiv})
    -- Implemented loading for animated WebP images.
        \end{itemize}
\section{Additional experience}
    \subsection{Software Engineering Group project -- designated "gitmaster"
    \hfill 2019-09 -- 2020-06}
        \begin{itemize}
            \item Organised the \emph{git} repository for the project's source
                code - Advanced \emph{version control}.
            \item Managed the ideas of a \emph{diverse group} of people to
                create a cohesive software solution to an \emph{industry
                challenge}.
        \end{itemize}
\section{Programming Languages}
\langa{
    C,
    C++,
    sh/bash,
    \LaTeX,
}\langb{
    Python,
    sed/AWK,
    Javascript,
    R,
}\langc{
    Groff (ms/man),
    SQL/NoSQL,
    Haskell,
}\langd{
    Perl,
    Java,
}\lange{
    Lua,
    PHP,
    C\#,
    \ldots
}
\section{Technologies}
\langa{
    Ansible,
    Vim,
    GNU/Linux,
    Make,
    Systemd,
}\langb{
    Git/svn,
    SSH,
    Docker[-compose],
    REST APIs (FastAPI/Express.js),
}\langc{
    GDB,
    Clang/LLVM,
    Proxmox VE,
}\langd{
    CMake,
    ARM architectures,
}\lange{
    QEMU/KVM,
    ZFS,
    Email (postfix, dovecot, OpenDKIM),
    \ldots
}
%\section{Languages}
%    \begin{itemize}
%        \item English (Native speaker)
%        \item Chinese - Mandarin (Learning)
%    \end{itemize}
\end{document}
